European or American? A re-examination of the transatlantic influence over the IMF

### 2025-09-06 manuscript/manuscript.qmd
Add summary stats as a section

## Model Specification {#sec-model}

>>>>

## Summary Statistics

We present summary statistics for key variables in @tbl-summary.

```{r}
#| label: tbl-summary
#| tbl-cap: Summary Statistics of Key Variables (1980–2010)
#| tbl-pos: H
library(modelsummary)
dsummary(
  (`IMF loan to GDP ratio` = imfloannew100) +
    (`IMF participation rate` = imf_p) +
    (`IMF loan approval` = imf5a) +
    (`Number of IMF conditions` = tc) +
    (`USA Influence` = us) +
    (`EUP Influence` = eu) +
    (`IMF Staff` = shstaffl) +
    (`IMF Quota` = `shquotal`) +
    (GDP = lnrgdpnew) +
    (GDPpc = rgdpchnew) +
    (`GDPpc growth` = growth1new) +
    (Reserves = reserv1) +
    (OECD = oecd1) ~ 
    Mean + SD + Min + (Q1 = P25) + Median + (Q3 = P75) + Max + N,
  data = dta
) |> tinytable::theme_latex(resize_width = 1, resize_direction = "down")
```

# Model Specification {#sec-model}
